simulation & inference of transients

### 2019-07-11 notebook/ghost-fit.Rmd
larger simulation set

```{r}
wide <- data %>% spread(reps, x) %>% select(-t) %>% 
  select(2) %>% # which / how many reps we use
  as.matrix()
n <- dim(wide)[1]

@@

```{r}
#bayesplot::mcmc_trace(draws)
```

>>>>

Divide this data into several groups based on

```{r}
means <- data %>% group_by(reps) %>% summarise(ave = mean(x)) %>% arrange(ave)

lows <- means %>% dplyr::slice(1:10) %>% pull(reps)
highs <- means %>% dplyr::slice((n()-10):n()) %>% pull(reps)
coding <- function(reps) case_when(
  reps %in% lows ~ "low",
  reps %in% highs ~ "high"
)
df <- data %>% mutate(coding = coding(reps)) %>% na.omit()
df %>% ggplot(aes(t, x, group=reps, color = coding)) + geom_line(alpha=0.5)

#means %>% ggplot(aes(ave)) + geom_histogram(binwidth = 0.02)

```{r}
wide <- data %>% 
  filter(reps %in% highs) %>%
  spread(reps, x) %>%
  select(-t) %>% 
  as.matrix()
n <- dim(wide)[1]

@@

```{r}
bayesplot::mcmc_trace(draws)
```

### 2019-07-11 notebook/ghost-sims.Rmd
larger simulation set

```{r}
library(tidyverse)
library(nimble)
```

```{r}
#a = 0.023
r = 0.05
p <- list(r = .05, K = 2, Q = 5, H = .38, sigma = .02, a=0.023, N = 1e3)
growth <- function(x, p) x * p$r * (1 - x / p$K)
consumption <- function(x,p) p$a * x ^ p$Q / (x^p$Q + p$H^p$Q)
```

@@

```{r}
library(nimble)
library(tidyverse)
# Define stochastic model in BUGS notation
may  <- nimble::nimbleCode({

  x[1] <- x0
  for(t in 1:(N-1)){
    # Determinstic mean looks like standard R
    mu[t] <- x[t] + x[t] * r * (1 - x[t] / K)  - a * x[t] ^ Q / (x[t] ^ Q + H ^ Q)
    # Note the use of ~ in BUGS to show 'distributed as normal' 
    y[t+1] ~ dnorm(mu[t], sd = sigma)
    x[t+1] <- max(y[t+1],0)
  }

})
model <- nimbleModel(may,constants = p, inits = list(x0 = 0.2))
cmodel <- model #compileNimble(model)
set.seed(123456)
simulate(cmodel)
df <- tibble(t = seq_along(cmodel$x), x = cmodel$x)
```

```{r}
df %>% ggplot(aes(t,x)) + geom_point()
df %>% write_csv("../data/ex.csv")
```

Let's do 100 replicates

```{r}
set.seed(123)

df <- map_dfr(1:100, 
  function(i){
    simulate(cmodel)
    tibble(t = seq_along(cmodel$x), x = cmodel$x, reps = i)
   })
```

```{r}
df %>% 
  #filter(t %in% seq(1000, 2000, by = 1)) %>% 
  ggplot(aes(t,x, group=reps)) + geom_line(alpha=.2)

df %>% write_csv("../data/reps.csv")
```

>>>>

```{r message = FALSE}
library(tidyverse)
library(furrr)
library(nimble)
```

```{r}
p <- list(r = .05, K = 2, Q = 5, H = .38, sigma = .02, a=0.023, N = 4e3, x0 = 0.2)
growth <- function(x, p) x * p$r * (1 - x / p$K)
consumption <- function(x, p) p$a * x ^ p$Q / (x^p$Q + p$H^p$Q)
```

@@

```{r}
may <- function(x, p) x + growth(x,p) - consumption(x,p)
#x + x * p$r * (1 - x / p$K)  - p$a * x ^ p$Q / (x ^ p$Q + p$H ^ p$Q)

stochastic_sim <- function(f, p){
  x <- numeric(p$N)
  x[1] <- p$x0
  dBt <- rnorm(p$N, 0, p$sigma)
  for(t in 1:(p$N-1)){
    x[t+1] <- max( 
                  f(x[t], p) + dBt[t],
                  0)
  }
  data.frame(t = 1:p$N, x)
}

det_sim <- function(f, p){
  x <- numeric(p$N)
  x[1] <- p$x0
  for(t in 1:(p$N-1)){
    x[t+1] <- f(x[t], p)
  }
  data.frame(t = 1:p$N, x)
}
```

```{r}
plan("multisession")
system.time({
  df <- future_map_dfr(1:500, function(reps) stochastic_sim(may, p), .id = "reps")
})

```

```{r}
det <- det_sim(may,p) %>% mutate(reps=1)
mean <- df %>% group_by(t) %>% summarise(x = mean(x)) %>% mutate(reps = 1)
```

```{r}
df %>% ggplot(aes(t, x, group=reps)) + 
  geom_line(alpha=0.1) +
  geom_line(data = det, color = "blue") + 
  geom_line(data = mean, color = "red")
```

```{r}
df %>% write_csv("../data/reps.csv")
```
